Limited information strategies for a topological proximal game

### 2015-05-14 phd/talks-and-presentations/2015-05-13-topological-proximal-game.tex
add topological proximal game talk for spring topology conference

\subtitle
{AMS Southeastern Sectional Meeting} % (optional)

@@

\institute[Auburn University] % (optional, but mostly needed)
{
  %\inst{1}%
  Department of Mathematics and Statistics\\
  Auburn University}
  %\and
  %\inst{2}%
  %Department of Theoretical Philosophy\\
  %University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[15-03-29] % (optional)
{March 29, 2015}

@@

  This game was brought to my attention due to this result: \cite{MR3239205}

>>>>

\subtitle
{Spring Topology Conference 2015} % (optional)

@@

\institute[Auburn, AL] % (optional, but mostly needed)
{
  %\inst{1}%
  Auburn, AL}
  %\and
  %\inst{2}%
  %Department of Theoretical Philosophy\\
  %University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[15-05-13] % (optional)
{May 13, 2015}

@@

  This game connects to a game of Gary Gruenhage: \cite{MR3239205}
